{\footnotesize
\begin{thebibliography}{99}
	\bibitem{bib:Modern_Physics} Bauer, W., and Gary D. Westfall. University Physics with Modern Physics. 2nd ed. Vol. 2. New York, NY: McGraw-Hill Companies, 2014. Print. 	
	
	\bibitem{bib:Methods_Of_Theoretical} Boas, Mary L. Mathematical Methods in the Physical Sciences. 3rd ed. New York: John Wiley \& Sons, 1984. Print. 
	
	\bibitem{bib:Planets_and_telescopes} Brown, Edward, comp. ``Planets And Telescopes." (2015): n. pag. Print. Michigan State University Department of Astronomy and Physics
	
	\bibitem{bib:AST304} Brown, Edward, comp. Astronomy 304 class handouts (2015): n. pag. Print. Michigan State University Department of Astronomy and Physics
	
	\bibitem{bib:StellarAstrophysics} Brown, Edward, comp. ``Stellar Astrophysics." (2015): n. pag. Print. Michigan State University Department of Astronomy and Physics
	
	\bibitem{bib:dictionary} http://www.dictionary.com
	
	\bibitem{bib:Griffiths} Griffiths, David J. Introduction to Electrodynamics. 4th ed. N.p.: Pearson India Education Services Pvt, 2015. Print. 
	
	\bibitem{bib:Griffiths_QM}  Griffiths, David J. Introduction to Quantum Mechanics. 2nd ed. Harlow: Pearson, 2014. Print. 
	
	\bibitem{bib:PeriodicTable} Helmenstine, Todd. Periodic Table of the Elements. sciencenotes.org. 2015.
	
	\bibitem{bib:Linnemann} Linnemann, Jim, Dr. Modern Physics Lecture Notes. 2016. PHY 215 lecture notes. Department of Physics and Astronomy, Michigan State University. 
	
	\bibitem{bib:AbstractNotes} Meierfrankenfeld, Ulrich. MTH 310 Lecture Notes Based on Hungerford, Abstract Algebra. N.p.: Department of Mathematics, Michigan State U, 2015. Print. 
	
	\bibitem{electronics} Plonus, Martin. Electronics and Communications for Scientists and Engineers. San Diego: Academic, 2001. Print. 
	
	\bibitem{bib:ReitzEMTheory} Reitz, John Richard. Foundations of Electromagnetic Theory. 4th ed. N.p.: Addison-Wesley, 1992. Print. 
	
	\bibitem{bib:Kittel_ThermalPhysics}  Kittel, Charles, and Herbert Kroemer. Thermal Physics. San Francisco: W.H. Freeman, 1980. Print.
	
	\bibitem{Nazarewicz_PHY802} Nazarewicz, Witek. "MSU PHY802 Lecture Slides." Survey of Nuclear Physics 802/492 Spring 2017. Michigan State University, n.d. Web. 31 Mar. 2017. 
	
	\bibitem{bib:Foundations_Of_Astrophysics} Ryden, Barbara Sue., and Bradley M. Peterson. Foundations of Astrophysics. San Francisco: Addison-Wesley, 2010. Print. 
	
	\bibitem{bib:elementTable} ``Table of Isotopic Masses and Natural Abundances." (n.d.): n. pag. NC State University. Web. ``https://www.ncsu.edu/chemistry/msf/pdf/IsotopicMass\_NaturalAbundance.pdf". 
	
	\bibitem{bib:Classical_Mechanics} Taylor, John R. Classical Mechanics. Sausalito, CA: U Science, 2005. Print. 
	
	\bibitem{bib:WolfrmAlpha} ``Wolfram$|$Alpha: Computational Knowledge Engine." N.p., n.d. Web. 2016 x
	
	\bibitem{bib:Wolfram} ``Wolfram MathWorld: The Web's Most Extensive Mathematics Resource." Wolfram MathWorld. N.p., n.d. Web. 
	
	\bibitem{DiffEQ} Zee, Dennis G. A first Course in Differential Equations with Modeling Applications." Edition 10. Book.
\end{thebibliography}
}
