\begin{center}
	\textbf{Preface}
\end{center}

This document is a compilation of useful programming formulations, definitions, constants, and general information used throughout my own schooling and research as a reference while furthering education. It's purpose is to provide a complete 'encyclopedia' per say of various codes, syntax and significant ideas used often. The idea and motivation behind it is to be a quick reference providing easily accessible access to necessary information for either double checking or recalling proper formulations or algorithms for use in various situations due to my own shortcomings in matters of memorization. All the material in this document was either directly copied from one of the references listed at the end or derived from scratch. On occasion typos may exist due to human error but will be corrected when discovered.
	
The version number is updated every time the document is distributed, printed, or referred to. This ensures that there is no two copies with different information and similar version numbers. The latest update date is automatically set to the current date each time the document is edited. Please refrain from distributing this handbook without permission from the original author/compiler. This book is formatted for printing.

For more information about this book or details about how to obtain your own copy please visit:
\begin{center}
	https://msu.edu/{\raise.17ex\hbox{$\scriptstyle\sim$}}torodean/AHandbook.html
\end{center}
\begin{center}
	\textbf{Disclaimer}
\end{center}

This book contains codes, formulas, definitions, and theorems that by nature are very precise. Due to this, some of the material in this book was taken directly from other sources. This is only such in cases where a change in wording or codes could cause ambiguities or loss of information quality.  Following this, all sources used are listed in the references section.